%%=============================================================================
%% Referenties
%%=============================================================================

\chapter*{\IfLanguageName{dutch}{Bibliografie}{Bibliography}}%
\label{ch:bibliografie}

% Ik heb manueel een lijst van referenties samengesteld die relevant zijn voor dit onderzoek. 
% Dit omdat het biber commando niet werkte in mijn LaTeX editor.

\begin{itemize}[label={}]
    \item Baker, H. (2021). Do identical twins have identical fingerprints? \textit{LiveScience}. Retrieved from \url{https://www.livescience.com/do-identical-twins-have-identical-fingerprints.html}
        
    \item Denniss, W., \& Bradley, J. (2017). OAuth 2.0 for Native Apps. \textit{RFC 8252}. Retrieved from \url{https://www.rfc-editor.org/info/rfc8252}
    
    \item Hardt, D. (2012). The OAuth 2.0 Authorization Framework. \textit{RFC 6749}. Retrieved from \url{https://www.rfc-editor.org/info/rfc6749}
    
    \item Jaiswal, R. K., \& Saxena, G. (2018). Biometric Recognition System (Algorithm). \textit{arXiv:1812.03385}. Retrieved from \url{https://doi.org/10.48550/arXiv.1812.03385}
    
    \item Jones, M. B., \& Hardt, D. (2012). The OAuth 2.0 Authorization Framework: Bearer Token Usage. \textit{RFC 6750}. Retrieved from \url{https://www.rfc-editor.org/info/rfc6750}
        
    \item Lee, C. K., Chang, C. C., Johar, A., Puwira, O., \& Roshidah, B. (2013). Fingerprint Changes and Verification Failure Among Patients With Hand Dermatitis. \textit{JAMA Dermatology, 149}(3), 294-299. Retrieved from \url{https://doi.org/10.1001/jamadermatol.2013.1425}
        
    \item Sakimura, N., Bradley, J., Jones, M., De Medeiros, B., \& Mortimore, C. (2014). OpenID Connect Core 1.0 incorporating errata set 1. \textit{The OpenID Foundation, Specification, 335}. Retrieved from \url{https://openid.net/specs/openid-connect-core-1_0.html}
    
    \item Sheffer, Y., Hardt, D., \& Jones, M. B. (2020). JSON Web Token Best Current Practices. \textit{RFC 8725}. Retrieved from \url{https://www.rfc-editor.org/info/rfc8725}
        
    \item Bakar, K. A. A., \& Haron, G. R. (2013). Adaptive authentication: Issues and challenges. In \textit{2013 World Congress on Computer and Information Technology (WCCIT)} (pp. 1-6). IEEE. Retrieved from \url{https://doi.org/10.1109/WCCIT.2013.6618657}
    
    \item Annadurai, C., Nelson, I., Devi, K. N., Manikandan, R., Jhanjhi, N. Z., Masud, M., \& Sheikh, A. (2022). Biometric Authentication-Based Intrusion Detection Using Artificial Intelligence Internet of Things in Smart City. \textit{Energies, 15}(19), 7430. Retrieved from \url{https://doi.org/10.3390/en15197430}
\end{itemize}